Stepwise Multiple Regressions

### 2021-02-04 Stepwise Multiple Regressions.Rmd
Update including interaction with effect score

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect)

@@

@@

@@

>>>>

@@

##Model Refining

@@

#Model - Interaction

The response variable is the interaction between effect and effect score

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect.score,
         effect_f)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

## Remove Charge + Dose (volume)

Remove dose(volume) - highest p value

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
~~3. Dose (volume)~~
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         # dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

## Remove Charge + Dose (volume) + Dose (mass)

Remove dose(volume) - highest p value

The model starts with the following independent variables: 
1. Dose (count)
~~2. Dose (mass)~~
~~3. Dose (volume)~~
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         # dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         # dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge_f, 
         particle_source_f,
         org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

@@

#Model - Log Transformed + Interaction

Doses (count, mass and volume), size (continuous), and exposure duration are all log transformed given histogram results. The response variable is the interaction between effect and effect score.

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge_f, 
         particle_source_f,
         org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

##Remove Particle Source

Doses (count, mass and volume), size (continuous), and exposure duration are all log transformed given histogram results. The response variable is the interaction between effect and effect score.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
10. Charge (negative/positive)
~~11. Particle Source~~
12. Organism Group - substitute for body right now

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge_f, 
         # particle_source_f,
         org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)

##Remove Particle Source + Organism Group

Doses (count, mass and volume), size (continuous), and exposure duration are all log transformed given histogram results. The response variable is the interaction between effect and effect score.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
10. Charge (negative/positive)
~~11. Particle Source~~
12. Organism Group - substitute for body right now

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge_f, 
         # particle_source_f,
         # org_f,
         effect_f,
         effect.score)

#Fit the full model
Full_Model <- lm(effect_f*effect.score ~., data = y)
